Direct Spectral Detection: A Cheap Method to Detect and Characterize Binary Systems

### 2015-10-22 paper/ms.tex
Fixed Sunkyung name, added acknowledgment for J.E. Lee.

\author{Kevin Gullikson \altaffilmark{1}}
\author{Adam Kraus \altaffilmark{1}}
\author{Sarah Dodson-Robinson \altaffilmark{2}}
\author{Daniel Jaffe \altaffilmark{1}}
\author{Jeong-Eun Lee \altaffilmark{3}}
\author{Gregory N. Mace \altaffilmark{1}}
\author{Phillip MacQueen \altaffilmark{1}}
\author{Sunkyunk Park \altaffilmark{3}}
\author{Andrew Riddle \altaffilmark{1}}

@@

\section*{Acknowledgements}
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship to Kevin Gullikson. We would like to thank Bill Cochran and Mike Endl for observing some of the spectra used in this project.

@@

Finally, we would like to thank the anonymous referee for numerous comments that improved the paper.

>>>>

\author{Kevin Gullikson \altaffilmark{1}}
\author{Adam Kraus \altaffilmark{1}}
\author{Sarah Dodson-Robinson \altaffilmark{2}}
\author{Daniel Jaffe \altaffilmark{1}}
\author{Jeong-Eun Lee \altaffilmark{3}}
\author{Gregory N. Mace \altaffilmark{1}}
\author{Phillip MacQueen \altaffilmark{1}}
\author{Sunkyung Park \altaffilmark{3}}
\author{Andrew Riddle \altaffilmark{1}}

@@

\section*{Acknowledgements}
This research has made use of the SIMBAD database, operated at CDS, Strasbourg, France, and of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
It was supported by a start-up grant to Adam Kraus as well as a University of Texas Continuing Fellowship to Kevin Gullikson. J.-E. Lee was supported by the Basic Science Research Program through the National Research Foundation of Korea (NRF) (grant No. NRF-2015R1A2A2A01004769) and the Korea
Astronomy and Space Science Institute under the R\&D program (Project No. 2015-1-320-18) supervised by the Ministry of Science, ICT and Future Planning.

@@

We would like to thank Bill Cochran and Mike Endl for observing some of the spectra used in this project. . Finally, we would like to thank the anonymous referee for numerous comments that improved the paper.
